Kindly Bent to Free Us

### 2019-11-11 kindly/sdtyping/extra.tex
Fixed typos and renamed reborrow-rule from 'Borrow' to 'Reborrow'.

In \cref{sdtyping}, we only gave a partial description of
the splitting and borrowing relations on environments,
$\lsplit C\E\E\E$ and $\lregion C{x}\E\E$.
The complete definitions are shown on \cref{fig:sd-splitting,fig:sd-borrowing}.
All the definitions are made in term of the inference version, which
returns a fresh constraints. The solving version then simply
uses entailment, as shown in rule {\sc ESplit-Check} and
{\sc EBorrow-Check}.
The remaining new rules are dedicated to iterating over the environment.

\cref{fig:contraints-environments-types} defines
the rewriting relation on environment constraints,
$\Cleq\E k \Crewrite C$, which rewrites a constraint of the form
$\Cleq\E k$ into $C$. It proceeds by iterating over the environment
and expending the constraints for each binding.
Suspended bindings are rejected ({\sc ConstrSusp}).
Borrow bindings directly use the annotated kind ({\sc ConstrBorrow}).
Other bindings uses the underlying type scheme ({\sc ConstrBinding}).
Type schemes are constrained by first inferring the kind, and then
emitting the constraint ({\sc ConstrSD} and {\sc ConstrI}).

>>>>

In \cref{sdtyping}, we only gave a partial description of
the splitting and borrowing relations on environments,
$\lsplit C\E\E\E$ and $\lregion C{x}\E\E$.
The complete definitions are shown on \cref{fig:sd-splitting,fig:sd-borrowing}.
All the definitions are made in term of the inference version, which
returns fresh constraints. The solving version then simply
uses entailment, as shown in rule {\sc ESplit-Check} and
{\sc EBorrow-Check}.
The remaining new rules are dedicated to iterating over the environment.

\cref{fig:contraints-environments-types} defines
the rewriting relation on environment constraints,
$\Cleq\E k \Crewrite C$, which rewrites a constraint of the form
$\Cleq\E k$ into $C$. It proceeds by iterating over the environment
and expanding the constraints for each binding.
Suspended bindings are rejected ({\sc ConstrSusp}).
Borrow bindings directly use the annotated kind ({\sc ConstrBorrow}).
Other bindings use the underlying type scheme ({\sc ConstrBinding}).
Type schemes are constrained by first inferring the kind, and then
emitting the constraint ({\sc ConstrSD} and {\sc ConstrI}).
